---
title: "TidyVerse Data 607"
author: "Wiktoria Gnojek"
date: "10/24/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
In this assignment, you’ll practice collaborating around a code project with GitHub.  

GitHub repository:https://github.com/acatlin/FALL2021TIDYVERSE

**Loading Library**
```{r}
library(tidyverse)
library(DT)
```
The data set chosen can be found at this url; https://www.kaggle.com/mysarahmadbhat/alcohol-consumption

In this data set, we will be looking at alcoholic consumption per country per type of alcohol.

It is important to note;

**Units:** Average serving sizes per person.

**Source:** World Health Organisation, Global Information System on Alcohol and Health (GISAH), 2010.

The csv generated from Kaggle can be found under this GitHub link; https://github.com/WiktoriaGnojek/TidyVerse-Part1/blob/main/drinks.csv

**Loading the CSV**

One of the first functions we are using is readr from the tidyverse package. 
```{r}

alcohol <- read.csv("https://raw.githubusercontent.com/WiktoriaGnojek/TidyVerse-Part1/main/drinks.csv")
alcohol %>%
  datatable()
```
Next we will be using functions from the dplyr and ggplot2 libraries.

Which countries consume more than 250 servings of beer?
```{r}
beer <- alcohol %>%
  select(country, beer_servings, spirit_servings) %>%
  filter(beer_servings >= 250) %>%
  arrange(desc(beer_servings))
head(beer)
ggplot(beer, aes(x = fct_reorder(country, beer_servings), 
                      y = beer_servings)) + 
  geom_col(fill = "lightblue") + 
  labs(x = "Country", y = "Beer Servings", 
      caption = "Countries with Beer Servings Equal to or Above 250") + 
  coord_flip()
```

Compare this to countries who consume more than 250 servings of spirits?
```{r}
spirits <- alcohol %>%
  select(country, spirit_servings, beer_servings) %>%
  filter(spirit_servings >= 250) %>%
  arrange(desc(spirit_servings))
head(spirits)
ggplot(spirits, aes(x = fct_reorder(country, spirit_servings), 
                      y = spirit_servings)) + 
  geom_col(fill = "lightblue") + 
  labs(x = "Country", y = "Spirit Servings", 
      caption = "Countries with Spirit Servings Equal to or Above 250") + 
  coord_flip()
```

More Tidyverse functions, this time we will be creating ratios. 

**Beer Vs. Spirits** 

Per countries with highest beer consumption, how many beer servings are there per spirit servings?
```{r}
beer <- beer %>%
  mutate(beer_to_spirits_ratio = (beer_servings/spirit_servings)) %>%
  arrange(desc(beer_to_spirits_ratio)) 
beer
```

**Spirits Vs. Beer** 

Per countries with highest spirit consumption, how many spirit servings are there per beer servings?
```{r}
spirits <- spirits %>%
  mutate(spirits_to_beer_ratio = (spirit_servings/beer_servings)) %>%
  arrange(desc(spirits_to_beer_ratio))
spirits
```

Is there an inverse relationship, what can this lead us to conclude? 
What would be the most efficient way to plot ratios or a relationship using ggplot2? 
Outliers? Is there a common patter?



